Concurrent Programming in Harmony

### 2020-12-27 book/paper.tex
Latest

\begin{figure}
\begin{code}
\begin{verbatim}
#states = 71 diameter = 5                                                                              ==== Safety violation ====
P0: __init__/()   [0-4,31-43] 43 { .count: 0, .done: [False, False] }
P1: incrementer/0 [5-8]        9 { .count: 0, .done: [False, False] }
P2: incrementer/1 [5-15]      15 { .count: 1, .done: [False, True ] }
P1: incrementer/0 [9-15]      15 { .count: 1, .done: [True,  True ] }
P3: main/()       [17-27]     27 { .count: 1, .done: [True,  True ] }
>>> Harmony Assertion (file=code/Up.hny, line=10) failed: 1
Open file:///Users/rvr/github/harmony.new/harmony.html for more information
\end{verbatim}
\end{code}
\caption{The text output of running Harmony on \autoref{fig:inc}.}
\label{fig:incoutput}
\end{figure}

@@

In our case, Harmony reports a safety violation, in particular it
reports that the assertion and that
\textit{count} has value 1 instead of 2.
Next it reports an execution that failed this assertion.
The program got to the faulty execution in 5 ``steps.''
The output has four columns:
\begin{enumerate}
\item The main method and argument of the thread;
\item The sequence of program counters of the HVM instructions that the thread executed;
\item The current program counter of the thread;
\item The contents of the shared memory.
\end{enumerate}

>>>>

\begin{figure}
\begin{code}
\begin{verbatim}
#states = 53 diameter = 5
==== Safety violation ====
T0: __init__() [0-4,31-46] 46 { count: 0, done[0]: False, done[1]: False }
T1: incrementer(0) [5-8]    9 { count: 0, done[0]: False, done[1]: False }
T2: incrementer(1) [5-15]  15 { count: 1, done[0]: False, done[1]: True  }
T1: incrementer(0) [9-15]  15 { count: 1, done[0]: True,  done[1]: True  }
T3: main()         [17-27] 27 { count: 1, done[0]: True,  done[1]: True  }
>>> Harmony Assertion (file=code/Up.hny, line=10) failed: 1
Open file:///Users/rvr/github/harmony/harmony.html for more information
\end{verbatim}
\end{code}
\caption{The text output of running Harmony on \autoref{fig:inc}.}
\label{fig:incoutput}
\end{figure}

@@

In our case, Harmony reports a safety violation, in particular it
reports that the assertion and that
\textit{count} has value 1 instead of 2.
Next it reports an execution that failed this assertion.
The program got to the faulty execution in 5 ``steps.''
The output has five columns:
\begin{enumerate}
\item A thread identifier;
\item The main method and argument of the thread;
\item The sequence of program counters of the HVM instructions that the thread executed;
\item The current program counter of the thread;
\item The contents of the shared memory.
\end{enumerate}
